On hyperparameter tuning through Lipschitz global optimization

### 2023-09-06 2023/ITMO paper/elsarticle-template-num.tex
fix two prepositions

The iOpt framework of intelligent optimization methods is designed to select optimal (in a given metric) values of parameters of complex objects and processes, especially artificial intelligence and machine learning methods. The framework allows fine-tuning of parameters of models and methods used in applied research in various fields of science.  The iOpt framework was designed in the Python programming language using its standard library. To use the framework, you need to have the Python interpreter version 3.8 or higher installed. The framework is open source and is available at \url{https://github.com/aimclub/iOpt}.

@@

\section*{Code availability}
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
Python scripts that reproduce the results of the presented experiments are available at \url{https://github.com/aimclub/iOpt/benchmarks}.

>>>>

The iOpt framework of intelligent optimization methods is designed to select optimal (in a given metric) values of parameters of complex objects and processes, especially in artificial intelligence and machine learning methods. The framework allows fine-tuning of parameters of models and methods used in applied research in various fields of science.  The iOpt framework was designed in the Python programming language using its standard library. To use the framework, you need to have the Python interpreter version 3.8 or higher installed. The framework is open source and is available at \url{https://github.com/aimclub/iOpt}.

@@

\section*{Code availability}
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.
Python scripts that reproduce the results of the experiments described in this paper are available at \url{https://github.com/aimclub/iOpt/benchmarks}.
